---
title: "QP Data Analysis"
author: "Diana Sanchez"
date: "March 2023"
output:
  html_document: default
  word_document: default
---


rm(list = ls(all.names = TRUE)) #clear R environment


# Load libraries
```{r message=FALSE, warning=FALSE , include=FALSE,echo =TRUE}
library(readr)
library(ggplot2)
library(GGally)
library(speakr)
library(dplyr)
library(tidyverse)
library(readr)
library(plyr)
library(stringi)
library(purrr)
library(broom)
library(scatterplot3d)
library(table1)

library(tidyr)
library(readr)
library(readxl)

library(patchwork)

library(lmtest)
library(AICcmodavg)

```



#Analysis of all_data 
## Tidy all_data
all_data df includes all 58 participants, two groups. Only total correct responses were included for each experimental task (flanker, stroop, backward). new_all_data excludes participant kbzo07 who was removed.
```{r message=FALSE, warning=FALSE , include=FALSE,echo =TRUE}
#Load working data
all_data <- read.csv("/Users/princesa/Desktop/diana/all_data.csv", header = TRUE)

#summary
summary(all_data)

#remove outlier No.45 (kbzo7)
new_all_data <- all_data[-c(45),]

#separate groups: nonLanguage teachers and language teachers
nonLanguage <- new_all_data[1:36, ]
language <- new_all_data[37:57, ]

nonLanguage$language = "NonLanguage" #add column "language" to indicate nonlanguage
language$language = "Language" #add column "language" to indicate language

#adding "language" column to indicate nonLanguage or language for each participant in all_data
new_all_data = bind_rows(nonLanguage,language)
```


##Standardize Age and IQ
```{r}
final_df = new_all_data %>% mutate(group_language = if_else(language == 'NonLanguage',-1,1),
            age_z = (age - mean(age)) / sd(age),
            iq_z = (IQ - mean(IQ)) / sd(IQ))
final_df
colnames(final_df)[7]='Bilingual'
```

## MODELS UPDATED March 27
# STROOP: Regression and Nested Model Comparison
```{r}
mod_0 <- lm(stroop_correct ~ group_language, final_df)
summary(mod_0)

AIC(mod_0) # 356.4777
BIC(mod_0) # 362.6068
```

```{r}
mod_1 <- lm(stroop_correct ~ group_language + age, final_df)
summary(mod_1)

AIC(mod_1) # 358.4629
BIC(mod_1) # 366.6351
```

```{r}
mod_2 <- lm(stroop_correct ~ group_language + age + IQ, final_df)
summary(mod_2)

AIC(mod_2) # 346.0536
BIC(mod_2) # 356.2689
```

```{r}
mod_3 <- lm(stroop_correct ~ group_language * age * IQ, final_df)
summary(mod_3)

AIC(mod_3) # 350.5537
BIC(mod_3) # 368.9412
```

```{r}
mod_4 <- lm(stroop_correct ~ group_language * age_z * iq_z, final_df)
summary(mod_4)

AIC(mod_4) # 350.5537
BIC(mod_4) # 368.9412
```

###Testing Models Backward Elimination
```{r}
anova(mod_2,mod_3) # Model 2 significant
anova(mod_1,mod_2) # Model 2 significant p=.0002

#For the Stroop task Model 2 is the best model
```

```{r}
anova(mod_0,mod_1) # Model 1 significant

anova(mod_3, mod_4) #Model 4 is standardized model
```

```{r}
models = list(mod_0, mod_1, mod_2, mod_3, mod_4) # put models in a list
model.names = c('model 0','model 1', 'model 2', 'model 3', 'model 4') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
##It states that Model 2 is the best for Stroop
```


# FLANKER: Regression and Nested Model Comparison
```{r}
mod_5 <- lm(flanker_correct ~ group_language, final_df)
summary(mod_5)

AIC(mod_5) # 356.4777
BIC(mod_5) # 362.6068
```

```{r}
mod_6 <- lm(flanker_correct ~ group_language + age, final_df)
summary(mod_6)

AIC(mod_6) # 379.4784
BIC(mod_6) # 387.6507
```

```{r}
mod_7 <- lm(flanker_correct ~ group_language + age + IQ, final_df)
summary(mod_7)

AIC(mod_7) # 374.1816
BIC(mod_7) # 384.3969
```

```{r}
mod_8 <- lm(flanker_correct ~ group_language * age * IQ, final_df)
summary(mod_8)

AIC(mod_8) # 369.9446
BIC(mod_8) # 388.332
```

```{r}
mod_9 <- lm(flanker_correct ~ group_language * age_z * iq_z, final_df)
summary(mod_9)

AIC(mod_9) # 369.9446
BIC(mod_9) # 388.332
```

###Testing Models Backward Elimination
```{r}
anova(mod_7,mod_8) # Model 8 significant p=.029
```

```{r}
anova(mod_6,mod_7) # Model 7 significant
anova(mod_5,mod_6) # Model 5 significant

anova(mod_8, mod_9) # Model 9 is standardized model
```

```{r}
models = list(mod_5, mod_6, mod_7, mod_8, mod_9) # put models in a list
model.names = c('model 5','model 6', 'model 7', 'model 8', 'model 9') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
##It states that Model 8, 9 is the best for Flanker (9 is the standarized model)
```


# BACKWARD: Regression and Nested Model Comparison
```{r}
mod_10 <- lm(backward_correct ~ group_language, final_df)
summary(mod_10)

AIC(mod_10) # 243.9676
BIC(mod_10) # 250.0967
```

```{r}
mod_11 <- lm(backward_correct ~ group_language + age, final_df)
summary(mod_11)

AIC(mod_11) # 245.451
BIC(mod_11) # 253.6232
```

```{r}
mod_12 <- lm(backward_correct ~ group_language + age + IQ, final_df)
summary(mod_12)

AIC(mod_12) # 237.0792
BIC(mod_12) # 247.2945
```

```{r}
mod_13 <- lm(backward_correct ~ group_language * age * IQ, final_df)
summary(mod_13)

AIC(mod_13) # 237.716
BIC(mod_13) # 256.1034
```

```{r}
mod_14 <- lm(backward_correct ~ group_language * age_z * iq_z, final_df)
summary(mod_14)

AIC(mod_14) # 237.716
BIC(mod_14) # 256.1034
```

###Testing Models Backward Elimination
```{r}
anova(mod_12,mod_13) # Model 12 significant
anova(mod_11,mod_12) # Model 12 significant p=.001
# For Backward Corsi, Model 12 is best model
```

```{r}
anova(mod_10,mod_11) # Model 10 significant

anova(mod_13, mod_14) # Model 14 is standardized model
```

```{r}
models = list(mod_10, mod_11, mod_12, mod_13, mod_14) # put models in a list
model.names = c('model 10','model 11', 'model 12', 'model 13', 'model 14') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
# It says model 12 is the best
```



##Plots for standardized age and IQ.
```{r}
plot1 <- final_df %>% 
  ggplot()+
  aes(x = age_z, y=flanker_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Flanker and Age") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot2 <- final_df %>% 
  ggplot()+
  aes(x = age_z, y=stroop_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Stroop and Age") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot3 <- final_df %>% 
  ggplot()+
  aes(x = age_z, y=backward_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Backward Corsi and Age") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

library(patchwork)
#(plot1 + plot_spacer() + plot2) / (plot_spacer() + plot3 + plot_spacer())  
plot1 / plot2  / plot3 
```

```{r}
plot4 <- final_df %>% 
  ggplot()+
  aes(x = iq_z, y=flanker_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Flanker and IQ") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot5 <- final_df %>% 
  ggplot()+
  aes(x = iq_z, y=stroop_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Stroop and IQ") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot6 <- final_df %>% 
  ggplot()+
  aes(x = iq_z, y=backward_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Backward Corsi and IQ") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

library(patchwork)
plot4 / plot5 / plot6
plot_layout(ncol = 2)
```



###OLD DATA 
#The information below is old data.
```{r}
m1 = lm(stroop_correct ~ group_language + age + IQ, final_df)
summary(m1) # 0.003503

par(mfrow = c(2,2)) 
plot(m1) 

AIC(m1) #346.0536
BIC(m1) #356.2689


m2 = lm(stroop_correct ~ group_language * age * IQ, final_df)
summary(m2) # 0.02313

par(mfrow = c(2,2)) 
plot(m2) 

AIC(m2) # 350.5537
BIC(m2) # 368.9412
# #Based on this output, we see that the AIC and BIC statistics are close but lower for m1 than for m2. This implies that the model fits are sufficiently close that neither can be preferred over the other.

m3 = lm(stroop_correct~group_language * age_z * iq_z, final_df)
summary(m3) # 0.02313

par(mfrow = c(2,2)) 
plot(m3) 

AIC(m3) # 350.5537
BIC(m3) # 368.9412
# The confidence intervals for AIC and BIC differences are exactly the same for m2 and m3 because both models have the same numbers of parameters.
```


```{r}
models = list(m1, m2, m3) # put models in a list
model.names = c('model 1', 'model 2', 'model 3') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
```


# Nested Model Comparisons
```{r}
anova(m1, m2, m3)

anova(m1, m2) # reject model 2

anova(m2, m3) # no pvalue

anova(m1, m3) # reject model 3

```

# ANOVA table
```{r}
anova_results1 = anova(m1, m2, m3)
anova_table1 = tidy(anova_results1)
print(anova_table1)

```

```{r}
jtest(m1,m2) # for nonnested model comparison

jtest(m1,m3)

jtest(m2,m3)
```


```{r}
m4 = lm(flanker_correct ~ group_language + age + IQ, final_df)
summary(m4)

par(mfrow = c(2,2)) 
plot(m4) 

AIC(m4) # 374.1816
BIC(m4) # 384.3969

m5 = lm(flanker_correct ~ group_language * age * IQ, final_df)
summary(m5)

par(mfrow = c(2,2)) 
plot(m5) 

AIC(m5) # 369.9446
BIC(m5) # 388.332

m6 = lm(flanker_correct~group_language * age_z * iq_z, final_df) #BEST model
summary(m6)

par(mfrow = c(2,2)) 
plot(m6) 

AIC(m6) # 369.9446
BIC(m6) # 388.332
```

```{r}
models = list(m4, m5, m6) # put models in a list
model.names = c('model 4', 'model 5', 'model 6') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
```

#Nested Model Comparisons using anova()
```{r}
anova(m4, m5, m6)

anova(m4, m5) # reject model 4
      
anova(m5, m6) # no pvalue

anova(m4, m6) # reject model 4
```

```{r}
anova_results2 = anova(m4, m5, m6)
anova_table2 = tidy(anova_results2)
print(anova_table2)

```

# Nested Model Comparisons using jtest
```{r}
jtest(m4,m5) # for nonnested model comparison

jtest(m5,m6)

jtest(m4,m6)
```

```{r}
m7 = lm(backward_correct ~ group_language + age + IQ, final_df)
summary(m7)

par(mfrow = c(2,2)) 
plot(m7) 

AIC(m7) # 237.0792
BIC(m7) # 247.2945

m8 = lm(backward_correct ~ group_language * age * IQ, final_df)
summary(m8)

par(mfrow = c(2,2)) 
plot(m8) 

AIC(m8) # 237.716
BIC(m8) # 256.1034

m9 = lm(backward_correct~group_language * age_z * iq_z, final_df)
summary(m9)

par(mfrow = c(2,2)) 
plot(m9) 

AIC(m9) # 237.716
BIC(m9) # 256.1034
```

```{r}
models = list(m7, m8, m9) # put models in a list
model.names = c('model 7', 'model 8', 'model 9') # named models for the AIC table
aictab(cand.set = models, modnames = model.names)
```

# Nested Model Comparisons
```{r}
anova(m7, m8, m9)

anova(m7, m8) # reject model 8
      
anova(m7, m9) # reject model 9

anova(m8, m9) # no pvalue,  

```

```{r}
jtest(m7,m8) # for nonnested model comparison

jtest(m8,m9)

jtest(m7,m9)
```



# plots Model 1 for Stroop task (best model)
```{r} 
plot7 <- final_df %>% 
  ggplot()+
  aes(x = age, y=flanker_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Flanker and Age") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot7


plot8 <- final_df %>% 
  ggplot()+
  aes(x = IQ, y=backward_correct,color=factor(group_language))+
  geom_point(size = 1) +
  ggtitle("Backward Corsi and IQ") + 
  geom_smooth(method = "lm") + 
  labs(color = "Language Group")+
  scale_color_manual(labels = c("NonLanguage","Language"),values = c("red","blue"))

plot8
```





## Background Questionnaire
```{r}
background_survey <- read.csv("~/Desktop/RStudio_QP/experiment_data/background_survey.csv", header = TRUE)
```

```{r }
str(background_survey)
background_survey$Age <- as.numeric(background_survey$Age)
background_survey_1  <- background_survey[1:57,] 

background_survey_1

#Reorganized years of experience in order on table
background_survey_1$Experience = factor(background_survey_1$Experience,levels = c('1-3 years', '4-6 years', '7-10 years', '11-15 years', '16+ years' ))

background_survey_1$Teaching_Level = factor(background_survey_1$Teaching_Level,levels = c('Kindergarten', '1st grade', '2nd grade', '3rd grade', '4th grade', '5th grade', '6-8 grades', '9-12 grades', '*Kindergarten-12th grades', 'College/University' ))
  
  

#table1(~Bilingual + Age + Ethnicity + Experience | Gender , data = background_survey_1) 
table1(~Age + Ethnicity + Experience + Residence + Teaching_Level | Gender , data = background_survey_1)

table1(~Bilingual + Age+Ethnicity | Gender , data = background_survey_1,topclass = "Rtable1-grid") # Puts table in square

table1(~Bilingual + Residence + Teaching_Level + Experience | Gender , data = background_survey_1) 


```
















